Free surface computations in mantle convection models

### 2016-04-27 free-surface-paper.tex
Add rayleigh_taylor script/figure
Fix reference.

\begin{equation}
\begin{aligned}
a_i(\Delta t) - a_i^{1} &= a_i(0) e^{-\Delta t/\tau_i} - a_i{(0)} \left[ 1 - \frac{\tau^*}{\tau_i} \left(1-e^{-\Delta t/\tau^*} \right) \right] \\
                        &= a_i{(0)} \left[ e^{-\Delta t/\tau_i} - 1 + \frac{\tau^*}{\tau_i} \left(1-e^{-\Delta t/\tau^*} \right) \right].
\end{aligned}
\end{equation}
Note that when $\tau_i = \tau^*$ the nonstandard finite difference scheme is exact.
The exponentials may be expanded to find
\ifdetail
\begin{equation}
a_i(\Delta t) - a_i^{1} = - a_i{(0)} \left[ \left(\frac{\Delta t}{\tau_i}\right)^2 - \frac{\tau^*}{\tau_i} \left(\frac{\Delta t }{\tau^* }\right)^2 \right].
\end{equation}
\fi
\begin{equation}
a_i(\Delta t) - a_i^{1} = {a_i{(0)} } \left( \frac{\Delta t}{\tau_i} \right)^2 \left( 1 - \frac{\tau_i}{\tau^*} \right) + O(\Delta t^3).
\end{equation}
Summing this error over many timesteps results in a factor of $\Delta t^{-1}$, demonstrating the first-order accuracy~\citep[e.g.]{leveque2007finite}.
The choice of $\tau^*$ controls the size of the coefficient on the truncation error for the scheme.
The error for a given mode becomes considerably smaller when $\tau^*$ is close to its natural relaxation times.

@@

>>>>

\begin{equation}
\begin{aligned}
a_i(\Delta t) - a_i^{1} &= a_i(0) e^{-\Delta t/\tau_i} - a_i{(0)} \left[ 1 - \frac{\tau^*}{\tau_i} \left(1-e^{-\Delta t/\tau^*} \right) \right] \\
                        &= a_i{(0)} \left[ e^{-\Delta t/\tau_i} - 1 + \frac{\tau^*}{\tau_i} \left(1-e^{-\Delta t/\tau^*} \right) \right].
\end{aligned}
\end{equation}
Note that when $\tau_i = \tau^*$ the nonstandard finite difference scheme is exact.
The exponentials may be expanded to find
\ifdetail
\begin{equation}
a_i(\Delta t) - a_i^{1} = - a_i{(0)} \left[ \left(\frac{\Delta t}{\tau_i}\right)^2 - \frac{\tau^*}{\tau_i} \left(\frac{\Delta t }{\tau^* }\right)^2 \right].
\end{equation}
\fi
\begin{equation}
a_i(\Delta t) - a_i^{1} = {a_i{(0)} } \left( \frac{\Delta t}{\tau_i} \right)^2 \left( 1 - \frac{\tau_i}{\tau^*} \right) + O(\Delta t^3).
\end{equation}
Summing this error over many timesteps results in a factor of $\Delta t^{-1}$, demonstrating the first-order accuracy~\citep[e.g.][]{leveque2007finite}.
The choice of $\tau^*$ controls the size of the coefficient on the truncation error for the scheme.
The error for a given mode becomes considerably smaller when $\tau^*$ is close to its natural relaxation times.

@@

\subsection{Connection with Dynamic Relaxation}
\label{sec:dynamic_relaxation}
